Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-03-24 ms.tex
All referee changes addressed (w/ Evan's tips)

%In Figure \ref{fig:entr_slice} we show a progression of entropy slices  for the 60-\Msun progenitor at 150 ms pb, for all values of $\Omega_0$.  As rotation becomes stronger, the entropy in the gain region decreases, reflecting the weakened convective activity.  
Furthermore, we recast our analysis by focusing on regions within the CCSN that emit GWs.  Albeit low GW amplitude, the lower panel of Figure \ref{fig:region} displays the inhibited convective signal with increasing rotation, as the GW signal in the gain region becomes increasingly muted.  The typical convective signals in the early post bounce regime are then quickly washed out by the post bounce ring down of the PNS, as rotation increases.

@@

>>>>

@@

Furthermore, we recast our analysis by focusing on regions within the CCSN that emit GWs.  \textcolor{red}{[10]Figure \ref{fig:region} displays the GW strain emitted from the 20 $M_\odot$ progenitor from the inner 50 km (upper panel) and from the region between 50 km and 150 km (lower panel) of the supernova.  The upper panel shows an initial, low frequency signal, independent of rotation within the first 60 ms post bounce.  This signal is typically characterized by prompt convection \citep{mueller:1997}.}  The lower panel of Figure \ref{fig:region} displays the inhibited convective signal \textcolor{red}{($t_{pb} > 100$ ms)} with increasing rotation, as the GW signal in the gain region becomes increasingly muted.  \textcolor{red}{\st{The typical convective signals in the early post bounce regime are then quickly washed out by the post bounce ring down of the PNS, as rotation increases.}}
